Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-02-11 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex

The value of $\beta$ can be estimated by first converting the apparent
permeability of a bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the
hydraulic conductivity $k_w$ using the conversion
in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to
$R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to
the native membrane permeability for water is $10^{-11}\le \beta\le
10^{-9}$. 
%
In our simulations the equilibrium shape of a semipermeable membrane in
open space is found to be independent of $\beta$ for
$10^{-4}\le\beta\le10^{-2}$. Within this range we find that $\beta$ only
affects the time it takes to reach the equilibrium membrane shape, which
is determined by the imposed flow, such as a quiescent flow, a linear
shear flow and its shear rate, and a Poiseuille flow and its maximum
velocity. From these results and our analysis of area dynamics, we
suspect similar hydrodynamics of a semipermeable inextensible membrane
with a smaller $\beta$ (as long as $\beta \neq 0$). On the other hand,
when $\beta\ge 10^{-1}$, we find that the membrane shape swells to
maximize the water content inside the membrane, independent of the
initial reduced area and the imposed flow in the far field. In the
simulations we focus on intermediate value of $10^{-5}\le \beta\le
10^{-3}$ to investigate the hydrodynamics of a semipermeable
inextensible membrane. 
%
Under strong confinement, $10^{-4}\le\beta\le10^{-3}$ is needed in our
simulations to keep the membrane tension below the threshold value for
membrane poration $\sim 10^{-3}$ N/m. Such range of $\beta$ may imply
that the lipid bilayer membrane would be porated under large stress
caused by confinement.

>>>>

The value of $\beta$ can be estimated by first
converting the apparent permeability of a 
bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
conductivity $k_w$ using the conversion
in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
\beta\le 10^{-9}$. 
%
In our simulations the equilibrium shape of a semipermeable membrane in open space is found to be independent of $\beta$ for $10^{-5}\le\beta\le10^{-2}$.
Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the background flow
(such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.)
From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable inextensible membrane 
with a smaller $\beta$ ($\beta\ne 0$). 
On the other hand,  when $\beta\ge 0.1$, we find that the membrane shape swells to maximize the water content inside the membrane, independent of the initial reduced 
area and the imposed flow in the far field.
In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
%
Under strong confinement, $10^{-4}\le\beta\le10^{-3}$ is needed in our
simulations to keep the membrane tension below the threshold value for
membrane poration $\sim 10^{-3}$ N/m. Such range of $\beta$ may imply
that the lipid bilayer membrane would be porated under large stress
caused by confinement.
